\documentclass[11pt, letterpaper]{memoir}
\usepackage{HomeworkStyle}

\begin{document}
	\begin{center}
		{\large	Quiz 12.1 -- Intermolecular Forces and Liquid Properties}
	\end{center}
	{\large Name: \rule[-1mm]{4in}{.1pt} 
	\subsection*{Question 1}
	State the strongest intermolecular force for each of the compounds below:
	
	\noindent {\Large \ch{CH2O} \hspace{2em} \ch{COOH} \hspace{2em} \ch{CO2} \hspace{2em} \ch{C6H14} \hspace{2em} \ch{CH2Cl2}\hspace{2em} \ch{CH3OH}}
	
	\vspace{3em}
	\subsection*{Question 2}
	From each pair of substances, circle the one with \emph{stronger} intermolecular forces:
	
	\noindent {\Large \ch{F2} ~|~ \ch{Cl2} \hspace{2em} \ch{C3H8} ~|~ \ch{C12H26} \hspace{2em} straight-chain \ch{C8H18} ~|~ branched \ch{C8H18}}
	
	\vspace{1em}
	\subsection*{Question 3}
	Provide an explanation for why liquids exhibit surface tension, from a microscopic perspective. You may find it useful to draw a simple diagram.
	
	\vspace{6em}
	\subsection*{Question 4}
	Soap bubbles take a tiny amount of water and stretch it out to form a very thin shell with both inner and outer surfaces. Compared to a droplet made from the same amount of water, a bubble has enormous surface area. Based on this information, do you predict that soap increases, or decreases the surface tension of water? Why?
	
	\vspace{4em}
	\subsection*{Question 5}
	Water in a glass vessel will form a concave meniscus, while mercury in a class vessel will form a convex meniscus. What can this tell you about the adhesive and cohesive forces in each case?
	
	\newpage
	\pagestyle{empty}
	\addtocounter{page}{-1}
	
	\section*{\emph{The Waves}}
	\paragraph{By Virginia Woolf}~
	
	\vspace{1em}
	\begin{minipage}{0.3\textwidth}
		\begin{center}
			I see nothing.
			
			We may sink and settle\\
			on the waves.\\
			The sea will drum\\
			in my ears.
			
			The white petals\\
			will be darkened\\
			with sea water.
			
			They will float\\
			for a moment\\
			and then sink.
			
			Rolling over\\
			the waves will\\
			shoulder me under.
			
			Everything falls in a\\
			tremendous shower,\\
			dissolving me.
		\end{center}
	\end{minipage}
\end{document}
