\documentclass[12pt, letterpaper]{memoir}
\usepackage{HomeworkStyle}

\begin{document}
	\begin{center}
		{\large	1210 Review Quiz}
	\end{center}
	{\large Name: \rule[-1mm]{4in}{.1pt} 
	\subsection*{Question 1}
	Give the number of protons, electrons, and neutrons in each atom or ion
	
	\begin{tabular}{c|c|c|c}
		& $e^-$ & $p^+$ & $n$ \\ \midrule
		\ch{^{27}Al} & ~\hspace{4em}~& ~\hspace{4em}~& ~\hspace{4em}~ \\ \midrule
		\ch{^{127}I-} &&&\\ \midrule
		\ch{^{40}Ca^{2+}}&&&
	\end{tabular}
	
	\vspace{2em}
	\subsection*{Question 2}
	A coffee-cup calorimeter contains $150.0~g$ of pure water. When $5.75~g$ of ammonium nitrate are added to the water, they dissolve and the solution temperature drops by $2.83~^\circ C$. What is the enthalpy of solvation for ammonium nitrate?
	
	% +25.69 kJ/mol
	\vspace{18em}
	\subsection*{Question 3}
	Give the name or formula for each of the following compounds. For molecular compounds, draw the correct Lewis structure:
	
	\begin{tabular}{ccc}
		Name & Formula & Lewis Structure\\ \\ \midrule \\
		Calcium Phosphate & \rule[-2pt]{8em}{1pt} & ~\hspace{5em}~\\ \\ \\
		\rule[-2pt]{8em}{1pt} & \ch{Mn2S3} \\ \\ \\
		Dinitrogen Trioxide & \rule[-2pt]{8em}{1pt} \\ \\ \\
		\rule[-2pt]{8em}{1pt} & \ch{SF6} \\ \\ \\
		Nitric acid & \rule[-2pt]{8em}{1pt} \\ \\ \\
		\rule[-2pt]{8em}{1pt} & \ch{H2SO3} \\ \\ \\
	\end{tabular}
	
	
	
	\vspace{2em}
	\subsection*{Question 4}
	Consider the thermite reaction: 
	
	\noindent 
	\rule[-2pt]{1em}{1pt} \ch{Fe2O3(s) +} \rule[-2pt]{1em}{1pt} \ch{Al(s) -> } \rule[-2pt]{1em}{1pt}\ch{Fe(l) +}\rule[-2pt]{1em}{1pt} \ch{Al2O3(s)} \hspace{2em} $\Delta H_{rxn} = -547.5~\dfrac{kJ}{mol}$
	
	Note the very exothermic enthalpy of this reaction, which leads to the iron product being molten. 
	
	\noindent $\circ$ First, balance this reaction
	
	\noindent $\circ$ If $2.5~g$ of \ch{Al} react with $5.0~g$ of \ch{Fe2O3}, how many $g$ of molten iron will be produced?
	
	\vspace{15em}
	\noindent $\circ$ How many $J$ of heat will be released?
	
	\vspace{6em}
	\subsection*{Question 5}
	Predict the products and write a balanced chemical equation for the reaction between sulfuric acid and aqueous calcium hydroxide.
	
	\newpage
	\pagestyle{empty}
	\addtocounter{page}{-1}
	\newgeometry{hmargin=0.85in}
	{\small
	\section*{\emph{When I Heard the Learn'd Astronomer}}
	\paragraph{By Walt Whitman}~
	
	\begin{verse}	
		When I heard the learn’d astronomer,\\	
		When the proofs, the figures, were ranged in columns before me,\\	
		When I was shown the charts and diagrams, to add, divide, and measure them,\\	
		When I sitting heard the astronomer where he lectured with much applause in the lecture-room,\\	
		How soon unaccountable I became tired and sick,\\	
		Till rising and gliding out I wander’d off by myself,\\	
		In the mystical moist night-air, and from time to time,\\	
		Look’d up in perfect silence at the stars.
	\end{verse}
	}
\end{document}
