\documentclass[11pt, letterpaper]{memoir}
\usepackage{HomeworkStyle}

\begin{document}
	\begin{center}
		{\large	Quiz 13.1 -- Saturation and Concentration}
	\end{center}
	{\large Name: \rule[-1mm]{4in}{.1pt} 
	
	\subsection*{Question 1}
	Fish require the right amount of dissolved oxygen to survive. If an arctic fish swims into tropical waters, will it suffer from oxygen deprivation or from oxygen poisoning?
	
	\vspace{2em}
	\subsection*{Question 2}
	The Henry's law constant for Oxygen is $0.0013~\dfrac{M}{atm}$. In Cedar City the atmospheric pressure is about $0.82~atm$ and the atmosphere is about $21\%$ oxygen. What is the molar concentration of oxygen in your glass of water in Cedar City?

	\vspace{2em}
	\subsection*{Question 3}
	A can of soda will begin to bubble as soon as you open it. Describe the state of the soda as soon as it is open, in terms of saturation, and explain why the bubbles are appearing.
	
	\vspace{4em}
	\subsection*{Question 4}
	A mixture contains $12.5~g$ of ethanol (\ch{C2H5OH}) in $85.0~g$ of water. Give the concentration in units of:
	\begin{itemize}
		\item $\dfrac{g}{g}$~:
		
		~
		\item $\%~by~Mass$~:
		
		~
		\item $Molality$~:
		
		~
		\item $\chi_{_{\ch{C2H5OH}}}$~:
		
		~
		\item $\chi_{_{\ch{H2O}}}$~:
	\end{itemize}

	\newpage
	\pagestyle{empty}
	\addtocounter{page}{-1}
	\section*{\emph{The Mortician in San Francisco}}
	\paragraph{By Randall Mann}~
	\begin{verse}
		This may sound queer,\\
		but in 1985 I held the delicate hands\\
		of Dan White:\\
		I prepared him for burial; by then, Harvey Milk\\
		was made monument—no, myth—by the years\\
		since he was shot.
		
		I remember when Harvey was shot:\\
		twenty, and I knew I was queer.\\
		Those were the years,\\
		Levi’s and leather jackets holding hands\\
		on Castro Street, cheering for Harvey Milk—\\
		elected on the same day as Dan White.
		
		I often wonder about Supervisor White,\\
		who fatally shot\\
		Mayor Moscone and Supervisor Milk,\\
		who was one of us, a Castro queer.\\
		May 21, 1979: a jury hands\\
		down the sentence, seven years—
		
		in truth, five years—\\
		for ex-cop, ex-fireman Dan White,\\
		for the blood on his hands;\\
		when he confessed that he had shot\\
		the mayor and the queer,\\
		a few men in blue cheered. And Harvey Milk?
		
		Why cry over spilled milk,\\
		some wondered, semi-privately, for years—\\
		it meant “one less queer.”\\
		The jurors turned to White.\\
		If just the mayor had been shot,\\
		Dan might have had trouble on his hands—
		
		but the twelve who held his life in their hands\\
		maybe didn’t mind the death of Harvey Milk;\\
		maybe, the second murder offered him a shot\\
		at serving only a few years.\\
		In the end, he committed suicide, this Dan White.\\
		And he was made presentable by a queer.
	\end{verse}
\end{document}
