\documentclass[11pt, letterpaper]{memoir}
\usepackage{HomeworkStyle}
\geometry{margin=0.75in}

\begin{document}
	\begin{center}
		{\large	Quiz 17.1 -- Buffer Solutions}
	\end{center}
	{\large Name: \rule[-1mm]{4in}{.1pt} 
	
	\subsection*{Question 1}
	Each acid/base conjugate pair can act as a buffer. \\Give the $pH$ range over which each pair below works (Consult Appendix A.3 for $K_a$ values):
	
	{\large \ch{NH4^+/NH3} \hspace{6em} \ch{HClO2/ClO2^-}\hspace{6em} \ch{HPO4^{2-}/PO4^{3-}}\hspace{6em} \ch{HC5H5N^+/C5H5N}}
	
	\vspace{2em}
	\subsection*{Question 2}
	$1.5~g$ of \ch{MgF2(s)} are dissolved in a $100.0~ml$ solution of $0.5~M$ \ch{HF}. Find the $pH$ of the solution assuming there is no volume change
	
	\vspace{6em}
	\subsection*{Question 3}
	Find the $pH$ if $25.0~ml$ of $0.75~M$ \ch{HCl} are added to the buffer solution prepared in Question 2
	
	\vspace{6em}
	\subsection*{Question 4}
	You want to make $200.0~ml$ of a buffer solution with $pH=9.750$ using a \ch{HCN/CN^-} buffer. You have one solution with $\left[\ch{HCN}\right]=0.100~M$ and another with $\left[\ch{CN^-}\right]=0.200~M$ which you can mix together to make the buffer. How many $ml$ of each should you use?
	
	\vspace{6em}
	\subsection*{Question 5}
	Find the buffer capacity of the solution prepared in Question 4 (How many moles of strong acid and strong base could be added before the $pH$ strays more than $1~pH$ unit from the $pK_a$)
	\newpage
	\newgeometry{margin=1.25in}
	\pagestyle{empty}
	\addtocounter{page}{-1}
\section*{\emph{My Voice}}
\paragraph{By Rafael Campo}~
\begin{verse}
	To cure myself of wanting Cuban songs,\\
	I wrote a Cuban song about the need\\
	For people to suppress their fantasies,\\
	Especially unhealthy ones. The song\\
	Began by making reference to the sea,\\
	Because the sea is like a need so great\\
	And deep it never can be swallowed. Then\\
	The song explores some common myths\\
	About the Cuban people and their folklore:\\
	The story of a little Carib boy\\
	Mistakenly abandoned to the sea;\\
	The legend of a bird who wanted song\\
	So desperately he gave up flight; a queen\\
	Whose strength was greater than a rival king’s.\\
	The song goes on about morality,\\
	And then there is a line about the sea,\\
	How deep it is, how many creatures need\\
	Its nourishment, how beautiful it is\\
	To need. The song is ending now, because\\
	I cannot bear to hear it any longer.\\
	I call this song of needful love my voice.
\end{verse}
\end{document}
