\documentclass[11pt, letterpaper]{memoir}
\usepackage{HomeworkStyle}
\geometry{margin=0.75in}

\begin{document}
	\begin{center}
		{\large	Quiz 19.2 -- Electrochemical Cells}
	\end{center}
	{\large Name: \rule[-1mm]{4in}{.1pt} 

\subsection*{Question 1}
 Write the cell notation for a voltaic cell made by reducing \ch{Fe^{2+}(aq)} to \ch{Fe(s)} and oxidizing \ch{Al(s)} to \ch{Al^{3+}(aq)}
 
 \vspace{4em}
 \subsection*{Question 2}
 Sketch the cell, labeling:
 \begin{itemize}
 	\item Anode
 	\item Cathode
 	\item Salt Bridge
 	\item Direction of electron flow
 	\item Direction of redox reactions
 	\item Direction of ion flow
 \end{itemize}

\vspace{12em}
\subsection*{Question 3}
Give the standard cell potential for this cell

\vspace{4em}
\subsection*{Question 4}
Is this a voltaic cell, or an electrolytic cell?
	\newpage
	\newgeometry{margin=1.25in}
	\pagestyle{empty}
	\addtocounter{page}{-1}
\newgeometry{hmargin=1.in,vmargin=1.25in}
\section*{\emph{O Me! O Life!}}
\paragraph{By Walt Whitman}~
\begin{verse}
	Oh me! Oh life! of the questions of these recurring,\\
	Of the endless trains of the faithless, of cities fill’d with the foolish,\\
	Of myself forever reproaching myself, (for who more foolish than I, and who more faithless?)\\
	Of eyes that vainly crave the light, of the objects mean, of the struggle ever renew’d,\\
	Of the poor results of all, of the plodding and sordid crowds I see around me,\\
	Of the empty and useless years of the rest, with the rest me intertwined,\\
	The question, O me! so sad, recurring—What good amid these, O me, O life?
	
	\hspace{9.5em}Answer.\\
	That you are here—that life exists and identity,\\
	That the powerful play goes on, and you may contribute a verse.
\end{verse}
\end{document}
